# Introducing Visual Analytics {#Chpt1}

This first chapter is meant to be an introduction to visual analytics.

## Admin and Course Introduction {#L1}

### Objectives

1. Introduce the course  
2. Understand classroom expectations  
3. Use R for some basic computations

Material discussed in class:

Why stats and probability? 

Math 377 course and purpose

Look at syllabus and due dates

### In Class Work

Load and use swirl

Demo R

Load a library and explain installing versus loading:

```{r eval=FALSE}
library(fastR)
```

Look at the structure of a dataframe.

```{r}
str(students)
```


You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

```{r eval=FALSE}
library(dplyr)
library(htmlwidgets)
library(rpivotTable)
library(crosstalk)
library(DT)
library(leaflet)
```


```{r}
DT::datatable(iris)
```

```{r eval=FALSE}
library(ggplot2)
library(plotly)
```

```{r}
p <- ggplot(data = diamonds, aes(x = cut, fill = clarity)) +
            geom_bar(position = "dodge")
ggplotly(p)
```

```{r}
data(mtcars)
rpivotTable(mtcars,rows="gear", cols=c("cyl","carb"),width="100%")
```

```{r eval=FALSE}
devtools::install_github("jcheng5/d3scatter")
```


```{r}
library(htmlwidgets)
library(crosstalk)
library(leaflet)
library(DT)
library(d3scatter)
```

```{r}
shared_mtcars <- SharedData$new(mtcars)
bscols(widths = c(3,NA,NA),
  list(
    filter_checkbox("cyl", "Cylinders", shared_mtcars, ~cyl, inline = TRUE),
    filter_slider("hp", "Horsepower", shared_mtcars, ~hp, width = "100%"),
    filter_select("auto", "Automatic", shared_mtcars, ~ifelse(am == 0, "Yes", "No"))
  ),
  d3scatter(shared_mtcars, ~wt, ~mpg, ~factor(cyl), width="100%", height=250),
  d3scatter(shared_mtcars, ~hp, ~qsec, ~factor(cyl), width="100%", height=250)
)
```

